Ontology Matching Paper

### 2016-05-08 milestone3/paper/paper.tex
more data linking stuff

\subsubsection{Linking the Cultural Dataset}
This dataset has a domain in part similar to our so the linking procedure
is trivial and reduces to a check on the \texttt{rdfs:label} and some other
property. An example Silk linkage rule is shown in Figure \ref{fig:link_event_g10}
that matches events; in this case the match is checked against
\texttt{rdfs:label} and \texttt{dc:title}.
%TODO link other entities

@@

\subsubsection{Linking the Tourist Safety Dataset}
In spite being about a different domain, this dataset can still be linked with
ours for what concerns events and locations / venues. Indeed the overlap between
events in this dataset and ours is big and we are able to match a big proportion
of entities by using a linkage rule similar to that shown in Figure
\ref{fig:link_event_g10} but using \texttt{rdfs:label} for both data sources.

\subsubsection{Linking the Activity Finding Dataset}
For events the linkage rule is less trivial and immediate than that for the
Cultural Dataset and involves the use of more properties and an aggregator as
shown in Figure \ref{fig:link_event_g15}.

>>>>

In the following sections we show how we implemented a Data Linking system to
link our dataset with three other datasets created by peers following our same
class\footnote{Knowledge Representation on the Web at VU Amsterdam, 2015/2016}.
Moreover we tried to look-up the Linked Open Data cloud searching for similar
datasets that we could link to ours. We used
LOTUS\footnote{\url{http://lotus.lodlaundromat.org/}}, a tool from the LOD
Laundromat suite\footnote{\url{http://lodlaundromat.org/}}\cite{beek2014lod}
that allows to search the LOD cloud for statements based on some query
parameters. Unfortunately we were not able to find interesting datasets there.

\subsubsection{Linking the Cultural Dataset}
This dataset has a domain in part similar to our so the linking procedure
is trivial and reduces to a check on the \texttt{rdfs:label} and some other
property. An example Silk linkage rule is shown in Figure \ref{fig:link_event_g10}
that matches events; in this case the match is checked against
\texttt{rdfs:label} and \texttt{dc:title}. With this rule we are able to create
15 links over 239 source and 479 target event entities.

@@

\subsubsection{Linking the Tourist Safety Dataset}
In spite being about a different domain, this dataset can still be linked with
ours for what concerns events and locations / venues. Indeed the overlap between
events in this dataset and ours is big and we are able to match a big proportion
of entities by using a linkage rule similar to that shown in Figure
\ref{fig:link_event_g10} but using \texttt{rdfs:label} for both data sources.
Using this linkage rule we are able to link 45 events and locations between the
two datasets.

\subsubsection{Linking the Activity Finding Dataset}
For events the linkage rule is less trivial and immediate than that for the
Cultural Dataset and involves the use of more properties and an aggregator as
shown in Figure \ref{fig:link_event_g15}. With this linkage rule we are able to
link 84 activities / events.
